\documentclass[10pt,a4paper,sans]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.4in, top=0.4in, bottom=0.4in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{multicol}

% --- COLORS ---
\definecolor{primary}{HTML}{2E5077} % Elegant Navy Blue
\definecolor{secondary}{HTML}{4A628A} % Lighter Slate
\definecolor{text}{HTML}{333333}    % Soft Black

% --- FONTS ---
\usepackage[default]{sourcesanspro}

% --- SECTION FORMATTING ---
\titleformat{\section}
  {\large\bfseries\color{primary}\uppercase}
  {}{0em}
  {}[\vspace{-1.2ex}\rule{\textwidth}{1pt}]
\titlespacing*{\section}{0pt}{1.2ex}{0.6ex}

% --- CUSTOM COMMANDS ---
\newcommand{\entry}[4]{
  \noindent\textbf{#1} \hfill \textbf{\color{secondary}#2} \\
  \textit{#3} \hfill \textit{#4} \par
  \vspace{0.1ex}
}

\newcommand{\project}[2]{
  \noindent\textbf{#1} \hfill \textit{#2} \par
  \vspace{0.1ex}
}

\begin{document}
\pagestyle{empty}
\color{text}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{\color{primary}Mubashir Ahmed}} \\
    \vspace{0.5ex}
    {\large \textbf{Full Stack Web Developer \& AI Solutions Architect}} \\
    \vspace{1ex}
    \small
    \faMapMarker* { Karachi, Pakistan} \quad $|$ \quad
    \faPhone* { +92-3378063440} \quad $|$ \quad
    \href{mailto:contact@mubashir.me}{\faEnvelope { contact@mubashir.me}} \quad $|$ \quad
    \href{https://mubashir.me}{\faGlobe { mubashir.me}} \quad $|$ \quad
    \href{https://linkedin.com/in/mubashirahmed23}{\faLinkedin { linkedin.com/in/mubashirahmed23}}
\end{center}

\vspace{-0.5ex}

% --- SUMMARY ---
\section*{Summary}
Results-driven Software Engineer with 4+ years of experience designing and deploying scalable web applications and AI-powered systems. Specialized in the intersection of full-stack engineering and applied artificial intelligence, with a focus on production-ready LLM solutions and RAG architectures. Proven track record of automating business processes and building cost-optimized, intelligent systems.

% --- EXPERIENCE ---
\section*{Experience}

\entry{Full Stack Engineer}{The Implant Engine}{Dec 2025 -- Present}{Remote}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Developed custom SaaS and white-label marketplace apps for healthcare automation.
    \item Built TIE Tools, a CRM business intelligence platform that automates reporting and saves employee time through intelligent data aggregation.
\end{itemize}

\vspace{1.5ex}

\entry{Web \& AI Chatbot Developer}{Upwork}{May 2023 -- Present}{Freelance}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Engineered agentic solutions including custom MCP servers and intelligent autonomous bots.
    \item Designed and built B2B/B2C SaaS platforms with a focus on intuitive UX and robust architecture.
\end{itemize}

\vspace{1.5ex}

\entry{AI Chatbot \& Web Developer}{Fiverr}{Mar 2022 -- Present}{Freelance}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Created UX-friendly AI apps, custom CRM tools, and scalable SaaS websites for diverse global clients.
\end{itemize}

% --- SELECTED PROJECTS ---
\section*{Selected Projects}

\project{TIE Tools (CRM Business Intelligence Platform)}{Automated Reporting System}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Engineered a platform built for organizations to automate reporting by integrating data from various sources (Google Ads, Meta Ads, GoHighLevel).
    \item Developed specialized tools for Account Managers, Quality Assurance, and Media Buyers to run reporting on autopilot.
\end{itemize}

\vspace{1.5ex}

\project{Funnel2Tunnel: Maritime Domain Expert Chatbot}{Next.js, Langchain, Pinecone, AWS}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Developed a SaaS trained on 800+ maritime documents with OCR scanning and multichat capabilities.
    \item Optimized cost-effective context management and vector embedding pipelines.
\end{itemize}

\vspace{1.5ex}

\project{Chat with SQL: A Text-to-SQL AI Chatbot}{Gemma 3 1B, PostgreSQL, Chroma}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Locally deployable pipeline enabling natural language interaction with PostgreSQL databases.
    \item Implemented cost-effective prompt engineering and efficient conversation history management.
\end{itemize}

% --- CORE EXPERTISE & SKILLS ---
\section*{Core Expertise}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0.1ex]
    \item \textbf{B2B/B2C SaaS \& Platform Engineering:} Architecting scalable, robust B2B and B2C SaaS platforms and custom white-label marketplace applications.
    \item \textbf{Advanced AI \& Agentic Solutions:} Developing intelligent bots, custom MCP servers, and multi-context RAG architectures for autonomous, real-time workflows.
    \item \textbf{Business Intelligence \& CRM Automation:} Building custom CRM platforms (like TIE Tools) that integrate multi-source marketing data to fully automate reporting and systemize operations.
    \item \textbf{Full-Stack \& Cloud Deployment:} Delivering cost-optimized, end-to-end solutions utilizing Next.js, the MERN stack, vector databases, and modern cloud infrastructure (GCP, AWS, Azure).
\end{itemize}
\vspace{0.5ex}
\noindent \textbf{Technical Skills:} JavaScript, Python, Dart, SQL, React, Node.js, MongoDB, PostgreSQL, Pinecone, Docker, Git.

% --- EDUCATION ---
\section*{Education}
\entry{Sindh Madressatul Islam University (SMIU)}{Karachi, Pakistan}{Bachelor of Science in Computer Science $|$ GPA: 3.4}{Aug 2021 -- Jun 2025}

% --- CERTIFICATIONS ---
\section*{Certifications \& Awards}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item \faGithub { GitHub Foundations (2024) \& GitHub Starstruck Badge}
    \item \faGraduationCap { LangChain Chat with Your Data - DeepLearning.AI}
    \item \faCertificate { Intermediate Node.js Certificate - HackerRank}
    \item \faTrophy { Falcon Hackathon Certificate \& Web Scraping in Python}
\end{itemize}

\end{document}